raptr: Representative and Adequate Prioritisation Toolkit in R

### 2016-09-30 code/rmarkdown/article.Rmd
+ make cmd fixes

# Data accessibility
The \texttt{raptr R} package can be downloaded from The Comphrehensive R Archive Network (\url{https://cran.r-project.org/}). All data, code, and results are stored in an online repository (\url{www.github.com/paleo13/raptr-manuscript}) to permit replication and validation of this study.

>>>>

# Data accessibility
The \texttt{raptr R} package can be downloaded from The Comphrehensive R Archive Network (\url{https://cran.r-project.org/}). All data, code, and results are stored in an online repository (\url{https://www.github.com/paleo13/raptr-manuscript}) to permit replication and validation of this study.
